---
title: "KHANDLE Codebook"
subtitle: "Cycle 1: Wave 4 Summary"
date: "01/10/2025"
output:
  pdf_document:
    toc: true
  word_document:
    toc: true
  html_document:
    toc: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r message=FALSE}
library(tidyverse)
library(haven)
library(epiDisplay)
library(readxl)
```

```{r load dataset}
path_to_box <- "C:/Users/josephfong/Box/"

# update to the most recent data release

n_transfer <- 16
folder_date <- "2025Jan10"
file_date <- str_remove_all(as_date(folder_date), "-")

path_to_folder <- paste0(
  "KHANDLE_coded_data/Raw_data_tables/All_Wave/transfer", n_transfer, 
  "_", folder_date, "/"
)

dat <- read_sas(
  paste0(path_to_box, path_to_folder, "khandle_all_waves_", file_date, ".sas7bdat"))


dat_w4 <- dat %>% filter(COHORT == 1) %>% 
  dplyr::select(STUDYID, starts_with("W4"), WAVE4, "W3_TO_W4_DAYS")
```

```{r load data dictionary, message=FALSE, warning=FALSE}
# load the data dictionary for variable name and variable description
dictionary <- read_excel(
  paste0(path_to_box, path_to_folder, 
         "KHANDLE_All_Waves_", file_date, "_Data_Dictionary.xlsx"), 
  .name_repair = "universal", 
  sheet = "Data Description") %>% 
  dplyr::select(
    all_of(c("PHI", "Variable.Name", "Variable.Label", 
             "Cycle.1.Format.Values", "Cycle.2.Format.Values"))
    # Note: choose the right format values to match the cohort/cycle
  ) %>% 
  rename("var_name" = "Variable.Name", 
         "var_desc" = "Variable.Label", 
         "values"  = "Cycle.2.Format.Values")
```


\pagebreak

Note:

For each variable, the following information is pulled from the dictionary:

*	Variable name
*	Variable description
*	Possible values and coding

A frequency table is generated to accompany most of the variables, with the 
following columns:

*	Frequency
*	%(NA+) and cum.%(NA+): relative and cumulative frequencies calculated from 
  including the NA’s in the total
*	%(NA-) and cum.%(NA-): relative and cumulative frequencies calculated from 
  excluding the NA’s from the total

If a variable is quantitative in nature, a histogram is used to replace the 
frequency table, accompanied by the number of NA’s. 

\pagebreak

```{r codebook function}
codebook <- function(data, var, categorical = TRUE, print.values = TRUE) {
  var_description <- dictionary %>% 
    filter(var_name == var) %>% 
    # dplyr::select(var_desc)
    pull(var_desc)
  # var_description <- as.character(var_description)
  var_values <- dictionary %>% 
    filter(var_name == var) %>% 
    # dplyr::select(values)
    pull(values)
  # var_values <- as.character(var_values)
  # print out information to be included in the codebook
  
  print(str_c(var, ": ", var_description))
  if (!is.na(var_values) & print.values) {print(var_values)}
  
  if(categorical) {
    # print the frequency table
    # with absolute, relative and cumulative frequencies
    print(str_c("Frequency table of ", var))
    tab1(data[var], graph = FALSE, cum.percent = TRUE) %>% print()
  } else {
    x <- data[var] %>% as_vector()
    na_count <- sum(is.na(x))
    na_perc <- round(na_count/length(x), digits = 3)
    print(str_c("NA Frequency: ", na_count, " (", 100*na_perc, "%)"))
    try(hist(x, main = NULL, xlab = paste(var)))
  }
  
  cat("\n\n")
}
```

## Wave Information

<br>

```{r wave 4 info}
W4_wave_info_vars <- c("WAVE4", "W4_ENROLLED", "W4_COMPLETED_AT", 
                       "W3_TO_W4_DAYS", "W4S_INTERVIEW", "W4_SURVEY_SUBMISSIONSTATUS", "W4_RECORD")
codebook(dat_w4, "WAVE4")
#codebook(dat_w4, "W4_ENROLLED") # Not in newest data release
codebook(dat_w4, "W4_COMPLETED_AT")
codebook(dat_w4, "W4S_INTERVIEW")
codebook(dat_w4, "W4_RECORD")
codebook(dat_w4, "W4_SURVEY_SUBMISSIONSTATUS")
codebook(dat_w4, "W3_TO_W4_DAYS", categorical = FALSE)
all_vars <- W4_wave_info_vars
```

\pagebreak

## Language

<br>

```{r language}
w4_language <- "W4_LANGUAGE"
codebook(dat_w4, w4_language)
all_vars <- c(all_vars, w4_language)
```

\pagebreak

## Age at Interview

<br>

```{r age at interview}
w4_age_at_intv <- "W4_INTERVIEW_AGE"
codebook(dat_w4, w4_age_at_intv, categorical = FALSE)
all_vars <- c(all_vars, w4_age_at_intv)
```

\pagebreak

<!-- ## Education -->

<!-- <br> -->

<!-- ```{r w2 education} -->
<!-- w4_edu_vars <- dat_w4 %>% names() %>% str_subset("W4_EDU|D_EDU") -->
<!-- for (var in w4_edu_vars) { -->
<!--   codebook(dat_w4, var) -->
<!-- } -->
<!-- all_vars <- c(all_vars, w4_edu_vars) -->
<!-- ``` -->

<!-- Names, towns, states and description of the majors are omitted here.  -->

<!-- ```{r w2 college} -->
<!-- w4_college_vars <- dat_w4 %>% names() %>% str_subset("W4_COLLEGE") -->
<!-- for (var in str_subset(w4_college_vars, "NAME|TOWN|STATE|DESC",  -->
<!--                        negate = TRUE)) { -->
<!--   codebook(dat_w4, var) -->
<!-- } -->
<!-- all_vars <- c(all_vars, w4_college_vars) -->
<!-- ``` -->

<!-- \pagebreak -->

## Self-Administered Questionnaire (SQX) - General

<br>

```{r sqx general}
w4_wave_sqx <- dat_w4 %>% names() %>% 
  str_subset("_SQX_COMPLETED|_COMMENTS_SAQXR|_SQX_METHOD")
  
for(var in w4_wave_sqx) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_wave_sqx)
```

\pagebreak

## SQX - Stressful Life Events

<br>

```{r sqx sle}
w4_wave_sqx_sle <- dat_w4 %>% names() %>% 
  str_subset("_SQX_SLE_")
  
for(var in w4_wave_sqx_sle) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_wave_sqx_sle)
```

\pagebreak

## SQX - Traumatic Life Events

<br>

```{r sqx tle}
w4_wave_sqx_tle <- dat_w4 %>% names() %>% 
  str_subset("_SQX_TLE_")
  
for(var in w4_wave_sqx_tle) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_wave_sqx_tle)
```

\pagebreak

## SQX - Coping Strategy

<br>

```{r sqx cs}
w4_wave_sqx_cc <- dat_w4 %>% names() %>% 
  str_subset("_SQX_CC_|_SQX_CS_")
  
for(var in w4_wave_sqx_cc) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_wave_sqx_cc)
```

\pagebreak

## SQX - Adverse Childhood Events

<br>

```{r sqx aces}
w4_wave_childhx_events_age <- dat_w4 %>% names() %>% 
  str_subset("_CHILDHX_EVENTS_AGE_")

w4_wave_childhx_events_cat <- dat_w4 %>% names() %>%
  str_subset("_CHILDHX_EVENTS_DKREFUSED_|_CHILDHX_EVENTS_YN_"  )
  
for(var in w4_wave_childhx_events_cat) {
  codebook(dat_w4, var)
}

for(var in w4_wave_childhx_events_age) {
  codebook(dat_w4, var, categorical = FALSE)
}
all_vars <- c(all_vars, w4_wave_childhx_events_age, w4_wave_childhx_events_cat)
```

\pagebreak

## SQX - Locus of Control

<br>

```{r self-administered questionnaire}
w4_wave_sqx_loc <- dat_w4 %>% names() %>% 
  str_subset("_SQX_LOC")
  
for(var in w4_wave_sqx_loc) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_wave_sqx_loc)
```

\pagebreak

## Trust in medical researchers

<br>

```{r trust in medical researchers}
w4_wave_timrs <- dat_w4 %>% names() %>% 
  str_subset("_TIMRS_")
  
for(var in w4_wave_timrs) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_wave_timrs)
```

\pagebreak

## Religiosity

<br>

```{r religiosity}
w4_wave_religion <- dat_w4 %>% names() %>% 
  str_subset("_RELIGION_")
  
for(var in w4_wave_religion) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_wave_religion)
```

\pagebreak

## Occupational History

<br>

```{r w4 occupational history}
w4_jobs_vars <- dat_w4 %>% names() %>% 
  str_subset("WORK|_EMP_|MILITARY") %>% 
  str_subset("VOLUNTEER|SQX", negate = TRUE) %>% 
  str_subset("AGE", negate = TRUE)
for(var in w4_jobs_vars) {
  codebook(dat_w4, var)
}
codebook(dat_w4, "W4_EMP_RETIRED_AGE", categorical = FALSE)
all_vars <- c(all_vars, w4_jobs_vars, "W4_EMP_RETIRED_AGE")
```

\pagebreak

## Volunteer Work

<br>

```{r}
w4_volunteer_vars <- dat_w4 %>% names() %>% str_subset("VOLUNTEER")
for(var in w4_volunteer_vars) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_volunteer_vars)
```

\pagebreak

## Other Current Activities

<br>

```{r}
w4_ca_vars <- dat_w4 %>% names() %>% str_subset("_CA_")
for(var in w4_ca_vars) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_ca_vars)
```

\pagebreak

<!-- ## Ethnicity -->

<!-- <br> -->

<!-- ```{r} -->
<!-- w4_ethn_vars <- dat_w4 %>% names() %>% str_subset("ETHNICITY|D_RACE") -->
<!-- for(var in w4_ethn_vars) { -->
<!--   codebook(dat_w4, var) -->
<!-- } -->
<!-- all_vars <- c(all_vars, w4_ethn_vars) -->
<!-- ``` -->

<!-- \pagebreak -->

<!-- ## Immigration -->

<!-- <br> -->

<!-- ```{r} -->
<!-- w4_immigration_vars <- dat_w4 %>% names() %>%  -->
<!--   str_subset("COUNTRY_BORN|US_STATE|MX_STATE|AGE_MOVED_US|D_AGE_IMMIGRATION|MOTHER|FATHER") -->

<!-- for(var in w4_immigration_vars[1:4]) { -->
<!--   codebook(dat_w4, var) -->
<!-- } -->
<!-- codebook(dat_w4, "W4_AGE_MOVED_US_AGE", categorical = FALSE) -->
<!-- for(var in w4_immigration_vars[6:15]) { -->
<!--   codebook(dat_w4, var) -->
<!-- } -->
<!-- codebook(dat_w4, "W4_D_AGE_IMMIGRATION", categorical = FALSE) -->
<!-- all_vars <- c(all_vars, w4_immigration_vars) -->
<!-- ``` -->

<!-- \pagebreak -->

<!-- ## Gender and Sexual Orientation -->

<!-- <br> -->

<!-- ```{r} -->
<!-- w4_gender_vars <- dat_w4 %>% names() %>% str_subset("GENDER|ORIENTATION") -->
<!-- for(var in w4_gender_vars) { -->
<!--   codebook(dat_w4, var) -->
<!-- } -->
<!-- all_vars <- c(all_vars, w4_gender_vars) -->
<!-- ``` -->

<!-- \pagebreak -->

## Residence

<br>

```{r}
w4_residence_vars <- dat_w4 %>% names() %>% str_subset("RESIDENCE")
for(var in w4_residence_vars) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_residence_vars)
```

\pagebreak

## Marital Status

<br>

```{r}
w4_marital_vars <- dat_w4 %>% names() %>% 
  str_subset("MARITAL|SPOUSE|DIVORCE|MARRIAGE")
for(var in w4_marital_vars) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_marital_vars)
```

\pagebreak

## Income and Financial Insecurity

<br>

```{r}
w4_income_vars <- dat_w4 %>% names() %>% str_subset("INCOME|INCMRANGE")
for(var in w4_income_vars) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_income_vars)
```

\pagebreak

<!-- ## Residence History and Schools Attended -->

<!-- <br> -->

<!-- Some variables (including street address, city, and state) are marked PHI in the  -->
<!-- dictionary, and therefore not summarized here.  -->

<!-- ```{r} -->
<!-- w4_res_vars <- dat_w4 %>% names() %>% str_subset("_RES_")  -->
<!-- w4_school_vars <- dat_w4 %>% names() %>% str_subset("_SCHOOL_")  -->
<!-- for(var in c(w4_res_vars, w4_school_vars)) { -->
<!--   codebook(dat_w4, var) -->
<!-- } -->
<!-- all_vars <- c(all_vars, w4_res_vars, w4_school_vars) -->
<!-- ``` -->

<!-- \pagebreak -->

## Discrimination - Everyday

<br>

```{r}
w4_disc_day_vars <- dat_w4 %>% names() %>% str_subset("DISC_DAY") 
for(var in c("W4_DISCRIMINATION", w4_disc_day_vars)) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, "W4_DISCRIMINATION", w4_disc_day_vars)
```

\pagebreak

<!-- ## Discrimination - Lifetime -->

<!-- <br> -->

<!-- ```{r} -->
<!-- w4_disc_life_vars <- dat_w4 %>% names() %>% str_subset("DISC_LIFE")  -->
<!-- for(var in w4_disc_life_vars) { -->
<!--   codebook(dat_w4, var) -->
<!-- } -->
<!-- all_vars <- c(all_vars, w4_disc_life_vars) -->
<!-- ``` -->

<!-- \pagebreak -->

<!-- ## Ladder -->

<!-- <br> -->

<!-- ```{r} -->
<!-- codebook(dat_w4, "W4_LADDER1") -->
<!-- all_vars <- c(all_vars, "W4_LADDER1") -->
<!-- ``` -->

<!-- \pagebreak -->

## Children

<br>

```{r}
w4_children_vars <- dat_w4 %>% names() %>% 
  str_subset("CHILDREN") %>% 
  str_subset("CHILDHX", negate = TRUE)
for(var in w4_children_vars) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_children_vars)
```

\pagebreak

<!-- ## Siblings -->

<!-- <br> -->

<!-- ```{r} -->
<!-- w4_siblings_vars <- dat_w4 %>% names() %>% str_subset("SIBLINGS")  -->
<!-- for(var in w4_siblings_vars) { -->
<!--   codebook(dat_w4, var) -->
<!-- } -->
<!-- all_vars <- c(all_vars, w4_siblings_vars) -->
<!-- ``` -->

<!-- \pagebreak -->

## Relatives

<br>

```{r}
w4_rel_vars <- dat_w4 %>% names() %>% str_subset("RELATIVES|_REL_") 
for(var in w4_rel_vars) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_rel_vars)
```

\pagebreak

## Friends

<br>

```{r}
w4_friends_vars <- dat_w4 %>% names() %>% str_subset("FRIENDS") 
for(var in w4_friends_vars) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_friends_vars)
```

\pagebreak

## Confidante

<br>

```{r}
w4_confidante_vars <- dat_w4 %>% names() %>% str_subset("CONFIDANTE") 
for(var in w4_confidante_vars) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_confidante_vars)
```

\pagebreak

<!-- ## Childhood Family History -->

<!-- <br> -->

<!-- ```{r} -->
<!-- w4_childhx_vars <- dat_w4 %>% names() %>% str_subset("CHILDHX") -->
<!-- w4_mat_pat_vars <- dat_w4 %>% names() %>% str_subset("MATERNAL|PATERNAL") -->
<!-- w4_gu_vars <- dat_w4 %>% names() %>% str_subset("GROWINGUP") -->
<!-- for(var in c(w4_childhx_vars, w4_mat_pat_vars, w4_gu_vars)) { -->
<!--   codebook(dat_w4, var) -->
<!-- } -->
<!-- all_vars <- c(all_vars, w4_childhx_vars, w4_mat_pat_vars, w4_gu_vars) -->
<!-- ``` -->

<!-- \pagebreak -->

## Health

<br>

```{r}
w4_equipment_vars <- dat_w4 %>% names() %>% str_subset("EQUIPMENT")
w4_gen_health_vars <- c("W4_HLTH_NO_PROC", "W4_MEM_NO_PROC", 
                        "W4_SEEN_DOC", "W4_SEEN_DOC_TEXT", 
                        "W4_CONCENTRATING", "W4_WALKING", "W4_DRESSING", 
                        "W4_ERRANDS")
for(var in c("W4_HEALTH", w4_gen_health_vars, w4_equipment_vars)) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_gen_health_vars, w4_equipment_vars, "W4_HEALTH")
```

\pagebreak

## COVID-Related Questions

<br>

```{r}
w4_covid_vars <- dat_w4 %>% names() %>% str_subset("COVID")
for(var in w4_covid_vars) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_covid_vars)
```

\pagebreak

## Activities of Daily Living

<br>

```{r}
w4_adl_vars <- dat_w4 %>% names() %>% str_subset("DAILY_LIVING|_COMMENTS_PHYS")
for(var in w4_adl_vars) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_adl_vars)
```

\pagebreak

## Physical Activity

<br>

```{r}
w4_pa_vars <- dat_w4 %>% names() %>% str_subset("_PA_") %>% 
   # need to make sure these SENAS vars don't end up in this section
  str_subset("SENAS_PA_SE|SENAS_PA_SEM", negate = TRUE)
for(var in w4_pa_vars) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_pa_vars)
```

\pagebreak

## Everyday Cognition

<br>

```{r}
w4_ecog_vars <- dat_w4 %>% names() %>% str_subset("_ECOG_")
for(var in w4_ecog_vars) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_ecog_vars)
```

\pagebreak

## Sleep

<br>

```{r}
w4_sleep_vars <- dat_w4 %>% names() %>% str_subset("_SLEEP_|BED|UP_MORNING")
for(var in w4_sleep_vars) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_sleep_vars)
```

\pagebreak

## Self-Assessed Sensory Impairment

<br>

```{r}
w4_sensimp_vars <- dat_w4 %>% names() %>% str_subset("_SENSIMP_")
for(var in w4_sensimp_vars) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_sensimp_vars)
```

\pagebreak

## Head Injury

<br>

```{r}
w4_headinj_vars <- dat_w4 %>% names() %>% str_subset("HEAD_INJURY")
w4_headtra_vars <- dat_w4 %>% names() %>% str_subset("HEAD_TRAUMA")
for(var in c(str_subset(w4_headinj_vars, "HOSP\\d"), "W4_HEAD_TRAUMA")) {
  codebook(dat_w4, var)
}
for (var in c(str_subset(w4_headinj_vars, "HOSP\\d", negate = TRUE), 
              w4_headtra_vars[-1])) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_headinj_vars, w4_headtra_vars)
```


\pagebreak

## Pain

<br>

```{r}
w4_pain_vars <- dat_w4 %>% names() %>% str_subset("PAIN")
for(var in w4_pain_vars) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_pain_vars)
```

\pagebreak

## Smoking

<br>

```{r}
w4_smk_vars <- dat_w4 %>% names() %>% str_subset("SMK")
for(var in w4_smk_vars) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_smk_vars)
```

\pagebreak

## Alcohol Consumption

<br>

```{r}
w4_alc_vars <- dat_w4 %>% names() %>% str_subset("ALC")
for(var in w4_alc_vars) {
  codebook(dat_w4, var)
}
all_vars <- c(all_vars, w4_alc_vars)
```

\pagebreak

## Physical Measurements

<br>

```{r}
w4_phys_vars <- dat_w4 %>% names() %>% str_subset("_PHYS_")
w4_phys_cat <- rep(TRUE, length(w4_phys_vars))
w4_phys_cat[c(1:6,12:14,20:22,33,37,38)] <- FALSE
for(i in 1:length(w4_phys_vars)) {
  codebook(dat_w4, w4_phys_vars[i], w4_phys_cat[i])
}
all_vars <- c(all_vars, w4_phys_vars)
```

\pagebreak

## NIH Toolbox

<br>

```{r}
w4_NIHTLBX_vars <- dat_w4 %>% names() %>% str_subset("NIHTLBX")
codebook(dat_w4, "W4_NIHTLBX_NIH_TOOLBOX")
codebook(dat_w4, "W4_NIHTLBX_LANGUAGE")
for(var in str_subset(w4_NIHTLBX_vars, "NIH_TOOLBOX|f|FORM|DCCS|PAT_COMP", 
                      negate = TRUE)) {
  codebook(dat_w4, var, categorical = FALSE)
}
for(var in str_subset(w4_NIHTLBX_vars, "dccs|pat_comp")) {
  codebook(dat_w4, var, categorical = TRUE)
}
all_vars <- c(all_vars, w4_NIHTLBX_vars)
```

\pagebreak

## SENAS

<br>

```{r}
w4_SENAS_vars <- dat_w4 %>% names() %>% str_subset("SENAS")
codebook(dat_w4, "W4_SENAS_SENAS")
codebook(dat_w4, "W4_SENAS_VMFORM")
codebook(dat_w4, "W4_SENAS_TELEPHONE")
for(var in str_subset(w4_SENAS_vars, "SENAS_SENAS|VMFORM|LSFORM|TELEPHONE", 
                      negate = TRUE)) {
  codebook(dat_w4, var, categorical = FALSE)
}
all_vars <- c(all_vars, w4_SENAS_vars)
```

\pagebreak

<!-- ## Cognitive Impairment Probabilities  -->

<!-- <br> -->

<!-- ```{r} -->
<!-- w4_COGIMP_PROB_vars <- dat_w4 %>% names() %>% str_subset("COGIMP_PROB") -->
<!-- for(var in w4_COGIMP_PROB_vars) { -->
<!--   codebook(dat_w4, var, categorical = FALSE) -->
<!-- } -->
<!-- all_vars <- c(all_vars, w4_COGIMP_PROB_vars) -->
<!-- ``` -->

<!-- \pagebreak -->

## Interviewer Comments

<br>

The labels for these categorical comment variables are long and many share 
the same labels. These labels are detailed at the end of this section. 

```{r}
w4_INTFDBK_vars <- dat_w4 %>% names() %>% str_subset("INTFDBK")
all_vars <- c(all_vars, w4_INTFDBK_vars)
var_values_list <- c()
for(var in w4_INTFDBK_vars) {
  codebook(dat_w4, var, print.values = FALSE)
  var_value <- dictionary %>% 
    filter(var_name == var) %>% 
    pull(values)
  var_values_list <- c(var_values_list, var_value)
}
var_values_label <- unique(var_values_list)
var_label_index <- c()
for (i in 1:length(var_values_list)) {
  var_label_index <- c(var_label_index, 
                       match(var_values_list[i], var_values_label))
}
```

Values Label for Interviewer Comments:

```{r}
for (i in 1:length(var_values_label)) {
  print(paste0("Label ", i))
  print(var_values_label[i])
  cat("\n\n")
}
```

```{r}
tibble(
  "Variable" = w4_INTFDBK_vars,
  "Values Label" = var_label_index
) %>% print(n = Inf)
```
\pagebreak

## Variables missing from this codebook

<br>

The following variables were not included in the codebook. Normally, only SUBJID should be the only variable not being tracked. Other variables are included here due to them being asked in Cycle 2, Wave 4, which uses the same naming convention as Cycle 1, Wave 4. We have omitted these variables from the codebook as they were never asked in Cycle 4. 
```{r check}
length(names(dat_w4))
names(dat_w4)[!names(dat_w4) %in% unique(all_vars)]
# all variables should be summarized in this codebook other than SUBJID
```