---
title: "KHANDLE Codebook"
subtitle: "Multiphasic Health Checkup (MHC) Summary"
# author: "Juliet Yixuan Zhou & Natalie Gradwohl"
date: "01/10/2025"
output:
  pdf_document:
    toc: false
  word_document:
    toc: false
  html_document:
    toc: false
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r message=FALSE}
library(tidyverse)
library(haven)
library(epiDisplay)
library(readxl)
library(lubridate)
```

```{r load dataset}
path_to_box <- "C:/Users/josephfong/Box/"

# update to the most recent data release

n_transfer <- 16
folder_date <- "2025Jan10"
file_date <- str_remove_all(as_date(folder_date), "-")

path_to_folder <- paste0(
  "KHANDLE_coded_data/Raw_data_tables/All_Wave/transfer", n_transfer, 
  "_", folder_date, "/"
)

dat <- read_sas(
  paste0(path_to_box, path_to_folder, "khandle_all_waves_", file_date, ".sas7bdat"))

dat_mhc <- dat %>% filter(COHORT == 1) %>% 
  dplyr::select(STUDYID, starts_with("mhc"))
```

```{r load data dictionary, message=FALSE, warning=FALSE}
# load the data dictionary for variable name and variable description
dictionary <- read_excel(
  paste0(path_to_box, path_to_folder, 
         "KHANDLE_All_Waves_", file_date, "_Data_Dictionary.xlsx"), 
  .name_repair = "universal", 
  sheet = "Data Description") %>% 
  dplyr::select(
    all_of(c("PHI", "Variable.Name", "Variable.Label", 
             "Cycle.1.Format.Values", "Cycle.2.Format.Values"))
    # Note: choose the right format values to match the cohort/cycle
  ) %>% 
  rename("var_name" = "Variable.Name", 
         "var_desc" = "Variable.Label", 
         "values"  = "Cycle.2.Format.Values")
```

\pagebreak

Note:

For each variable, the following information is pulled from the dictionary:

*	Variable name
*	Variable description
*	Possible values and coding

A frequency table is generated to accompany most of the variables, with the 
following columns:

*	Frequency
*	%(NA+) and cum.%(NA+): relative and cumulative frequencies calculated from 
  including the NA’s in the total
*	%(NA-) and cum.%(NA-): relative and cumulative frequencies calculated from 
  excluding the NA’s from the total

If a variable is quantitative in nature, a histogram is used to replace the 
frequency table, accompanied by the number of NA’s. 

\pagebreak

```{r codebook function}
codebook <- function(data, var, categorical = TRUE, print.values = TRUE) {
  var_description <- dictionary %>% 
    filter(var_name == var) %>% 
    # dplyr::select(var_desc)
    pull(var_desc)
  # var_description <- as.character(var_description)
  var_values <- dictionary %>% 
    filter(var_name == var) %>% 
    # dplyr::select(values)
    pull(values)
  # var_values <- as.character(var_values)
  # print out information to be included in the codebook
  
  print(str_c(var, ": ", var_description))
  if (!is.na(var_values) & print.values) {print(var_values)}
  
  if(categorical) {
    # print the frequency table
    # with absolute, relative and cumulative frequencies
    print(str_c("Frequency table of ", var))
    tab1(data[var], graph = FALSE, cum.percent = TRUE) %>% print()
  } else {
    x <- data[var] %>% as_vector()
    na_count <- sum(is.na(x))
    na_perc <- round(na_count/length(x), digits = 3)
    print(str_c("NA Frequency: ", na_count, " (", 100*na_perc, "%)"))
    try(hist(x, main = NULL, xlab = paste(var)))
  }
  
  cat("\n\n")
}
```


```{r mhc}
for (var in str_subset(
  names(dat_mhc)[-1], 
  "BMI|CHOL|DIASTOLIC|SYSTOLIC|EXAM_AGE|GLUCOSE|FASTING|HEIGHT|WEIGHT")) {
  codebook(dat_mhc, var, categorical = FALSE)
}

for (var in str_subset(
  names(dat_mhc)[-1], 
 "BMI|CHOL|DIASTOLIC|SYSTOLIC|EXAM_AGE|GLUCOSE|FASTING|HEIGHT|WEIGHT", 
  negate = TRUE)) {
  codebook(dat_mhc, var)
}
```
