---
title: "KHANDLE Codebook"
subtitle: "Cycle 2: Wave 1 Summary"
# author: "Juliet Yixuan Zhou & Natalie Gradwohl"
date: "01/10/2025"
output:
  pdf_document:
    toc: true
  word_document:
    toc: true
  html_document:
    toc: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r message=FALSE}
library(tidyverse)
library(haven)
library(epiDisplay)
library(readxl)
```

```{r load dataset}
path_to_box <- "C:/Users/josephfong/Box/"

# update to the most recent data release

n_transfer <- 16
folder_date <- "2025Jan10"
file_date <- str_remove_all(as_date(folder_date), "-")

path_to_folder <- paste0(
  "KHANDLE_coded_data/Raw_data_tables/All_Wave/transfer", n_transfer, 
  "_", folder_date, "/"
)

dat <- read_sas(
  paste0(path_to_box, path_to_folder, "khandle_all_waves_", file_date, ".sas7bdat"))


dat_w1_c2 <- dat %>% filter(COHORT == 2) %>% 
  dplyr::select(STUDYID, starts_with("W1"), WAVE1)
```

```{r load data dictionary, message=FALSE, warning=FALSE}
# load the data dictionary for variable name and variable description
dictionary <- read_excel(
  paste0(path_to_box, path_to_folder, 
         "KHANDLE_All_Waves_", file_date, "_Data_Dictionary.xlsx"), 
  .name_repair = "universal", 
  sheet = "Data Description") %>% 
  dplyr::select(
    all_of(c("PHI", "Variable.Name", "Variable.Label", 
             "Cycle.1.Format.Values", "Cycle.2.Format.Values"))
    # Note: choose the right format values to match the cohort/cycle
  ) %>% 
  rename("var_name" = "Variable.Name", 
         "var_desc" = "Variable.Label", 
         "values"  = "Cycle.2.Format.Values")
```


\pagebreak

Note:

For each variable, the following information is pulled from the dictionary:

*	Variable name
*	Variable description
*	Possible values and coding

A frequency table is generated to accompany most of the variables, with the 
following columns:

*	Frequency
*	%(NA+) and cum.%(NA+): relative and cumulative frequencies calculated from 
  including the NA’s in the total
*	%(NA-) and cum.%(NA-): relative and cumulative frequencies calculated from 
  excluding the NA’s from the total

If a variable is quantitative in nature, a histogram is used to replace the 
frequency table, accompanied by the number of NA’s. 

\pagebreak

```{r codebook function}
codebook <- function(data, var, categorical = TRUE, print.values = TRUE) {
  var_description <- dictionary %>% 
    filter(var_name == var) %>% 
    # dplyr::select(var_desc)
    pull(var_desc)
  # var_description <- as.character(var_description)
  var_values <- dictionary %>% 
    filter(var_name == var) %>% 
    # dplyr::select(values)
    pull(values)
  # var_values <- as.character(var_values)
  # print out information to be included in the codebook
  
  print(str_c(var, ": ", var_description))
  if (!is.na(var_values) & print.values) {print(var_values)}
  
  if(categorical) {
    # print the frequency table
    # with absolute, relative and cumulative frequencies
    print(str_c("Frequency table of ", var))
    tab1(data[var], graph = FALSE, cum.percent = TRUE) %>% print()
  } else {
    x <- data[var] %>% as_vector()
    na_count <- sum(is.na(x))
    na_perc <- round(na_count/length(x), digits = 3)
    print(str_c("NA Frequency: ", na_count, " (", 100*na_perc, "%)"))
    try(hist(x, main = NULL, xlab = paste(var)))
  }
  
  cat("\n\n")
}
```

## Wave Information

<br>

```{r wave 1 info}
W1_wave_info_vars <- c("WAVE1", "W1_COMPLETED_AT", "W1_SURVEY_SUBMISSIONSTATUS",
                       "W1_SURVEY_TYPE")

for (var in W1_wave_info_vars) {
  codebook(dat_w1_c2, var)
}
all_vars <- W1_wave_info_vars
```

\pagebreak

## Language

<br>

```{r language}
w1_language <- "W1_LANGUAGE"
codebook(dat_w1_c2, w1_language)
all_vars <- c(all_vars, w1_language)
```

\pagebreak

## Age at Interview

<br>

```{r age at interview}
w1_age_at_intv <- "W1_INTERVIEW_AGE"
codebook(dat_w1_c2, w1_age_at_intv, categorical = FALSE)
all_vars <- c(all_vars, w1_age_at_intv)
```

\pagebreak

## Education

<br>

```{r w2 education}
w1_c2_edu_vars <- dat_w1_c2 %>% names() %>% str_subset("W1_EDU|D_EDU")
for (var in w1_c2_edu_vars) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_c2_edu_vars)
```

<!-- Names, towns, states and description of the majors are omitted here.  -->

<!-- ```{r w2 college} -->
<!-- w1_college_vars <- dat_w1_c2 %>% names() %>% str_subset("W1_COLLEGE") -->
<!-- for (var in str_subset(w1_college_vars, "NAME|TOWN|STATE|DESC",  -->
<!--                        negate = TRUE)) { -->
<!--   codebook(dat_w1_c2, var) -->
<!-- } -->
<!-- all_vars <- c(all_vars, w1_college_vars) -->
<!-- ``` -->

<!-- \pagebreak -->

## Occupational History

<br>

```{r w1 occupational history}
w1_c2_jobs_vars <- dat_w1_c2 %>% names() %>% 
  str_subset("WORK|JOB|_EMP_|MILITARY") %>% 
  str_subset("VOLUNTEER", negate = TRUE) %>% 
  str_subset("AGE", negate = TRUE) %>% 
  # filtering out things in cycle 1 only
  str_subset("JOB_MAIN|JOB_RECENT|FIRST", negate = TRUE)
for(var in w1_c2_jobs_vars) {
  codebook(dat_w1_c2, var)
}
codebook(dat_w1_c2, "W1_EMP_RETIRED_AGE", categorical = FALSE)
all_vars <- c(all_vars, w1_c2_jobs_vars, "W1_EMP_RETIRED_AGE")
```

\pagebreak

<!-- ## Occupational Complexity -->

<!-- <br> -->

<!-- ```{r w1 occupational complexity} -->
<!-- w1_c2_occ_comp_scores <- dat_w1_c2 %>% names() %>%  -->
<!--   str_subset("_JOB_") %>%  -->
<!--   str_subset("VOLUNTEER", negate = TRUE) %>%  -->
<!--   str_subset("_ASC|_DESC|_SC|_PD|_MS|_UWC") -->

<!-- w1_c2_occ_comp_other <- dat_w1_c2 %>% names() %>%  -->
<!--   str_subset("_JOB_") %>%  -->
<!--   str_subset("") -->
<!--   str_subset("VOLUNTEER", negate = TRUE) -->
<!-- for(var in w1_c2_jobs_vars) { -->
<!--   codebook(dat_w1_c2, var) -->
<!-- } -->
<!-- codebook(dat_w1_c2, "W1_EMP_RETIRED_AGE", categorical = FALSE) -->
<!-- all_vars <- c(all_vars, w1_c2_jobs_vars, "W1_EMP_RETIRED_AGE") -->
<!-- ``` -->

<!-- \pagebreak -->


## Volunteer Work

<br>

```{r}
w1_volunteer_vars <- dat_w1_c2 %>% names() %>% str_subset("VOLUNTEER")
for(var in w1_volunteer_vars) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_volunteer_vars)
```

\pagebreak

## Other Current Activities

<br>

```{r}
w1_ca_vars <- dat_w1_c2 %>% names() %>% str_subset("_CA_")
for(var in w1_ca_vars) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_ca_vars)
```

\pagebreak

## Ethnicity

<br>

```{r}
w1_c2_ethn_vars <- dat_w1_c2 %>% names() %>% str_subset("ETHNICITY|D_RACE")
for(var in w1_c2_ethn_vars) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_c2_ethn_vars)
```

\pagebreak

## Immigration

<br>

```{r}
w1_c2_immigration_vars <- dat_w1_c2 %>% names() %>%
  str_subset("COUNTRY_BORN|US_STATE|MX_STATE|AGE_MOVED_US|D_AGE_IMMIGRATION|MOTHER|FATHER")

for(var in w1_c2_immigration_vars[1:4]) {
  codebook(dat_w1_c2, var)
}
codebook(dat_w1_c2, "W1_AGE_MOVED_US", categorical = FALSE)
for(var in w1_c2_immigration_vars[6:23]) {
  codebook(dat_w1_c2, var)
}
codebook(dat_w1_c2, "W1_D_AGE_IMMIGRATION", categorical = FALSE)
all_vars <- c(all_vars, w1_c2_immigration_vars)
```

\pagebreak

## Gender and Sexual Orientation

<br>

```{r}
w1_gender_vars <- dat_w1_c2 %>% names() %>% str_subset("GENDER|ORIENTATION")
for(var in w1_gender_vars) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_gender_vars)
```

\pagebreak

## Residence

<br>

```{r}
w1_residence_vars <- dat_w1_c2 %>% names() %>% str_subset("RESIDENCE")
for(var in w1_residence_vars) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_residence_vars)
```

\pagebreak

## Marital Status

<br>

```{r}
w1_marital_vars <- dat_w1_c2 %>% names() %>% 
  str_subset("MARITAL|SPOUSE|DIVORCE|MARRIAGE")
for(var in w1_marital_vars) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_marital_vars)
```

\pagebreak

## Income and Financial Insecurity

<br>

```{r}
w1_income_vars <- dat_w1_c2 %>% names() %>% str_subset("INCOME")
for(var in w1_income_vars) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_income_vars)
```

\pagebreak

## Residence History and Schools Attended

<br>

Some variables (including street address, city, and state) are marked PHI in the
dictionary, and therefore not summarized here.

```{r}
w1_res_vars <- dat_w1_c2 %>% names() %>% str_subset("_RES_") 
w1_school_vars <- dat_w1_c2 %>% names() %>% str_subset("_SCHOOL_") %>%
  str_subset("_CTY_TEXT|_SCH_TEXT", negate = T)
for(var in c(w1_res_vars, w1_school_vars)) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_res_vars, w1_school_vars)
```

\pagebreak

## Childhood and parental edu

```{r}
w1_c2_mat_pat_vars <- dat_w1_c2 %>% names() %>% str_subset("MATERNAL|PATERNAL")
w1_c2_gu_vars <- dat_w1_c2 %>% names() %>% str_subset("GROWINGUP|CHILDHX") %>%
  str_subset("EVENTS", negate = T)
for(var in c(w1_c2_mat_pat_vars, w1_c2_gu_vars)) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_c2_mat_pat_vars, w1_c2_gu_vars)
```

\pagebreak


## Discrimination - Everyday

<br>

```{r}
w1_disc_day_vars <- dat_w1_c2 %>% names() %>% str_subset("DISC_DAY") 
for(var in c("W1_DISCRIMINATION", w1_disc_day_vars)) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, "W1_DISCRIMINATION", w1_disc_day_vars)
```

\pagebreak

## Discrimination - Lifetime

<br>

```{r}
w1_disc_life_vars <- dat_w1_c2 %>% names() %>% str_subset("DISC_LIFE") 
for(var in w1_disc_life_vars) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_disc_life_vars)
```

\pagebreak

## Ladder

<br>

```{r}
codebook(dat_w1_c2, "W1_LADDER1")
all_vars <- c(all_vars, "W1_LADDER1")
```

\pagebreak

## Children

<br>

```{r}
w1_children_vars <- dat_w1_c2 %>% names() %>% 
  str_subset("CHILDREN") %>% 
  str_subset("CHILDHX", negate = TRUE)
for(var in w1_children_vars) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_children_vars)
```

\pagebreak

## Siblings

<br>

```{r}
w1_siblings_vars <- dat_w1_c2 %>% names() %>% str_subset("SIBLINGS")
for(var in w1_siblings_vars) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_siblings_vars)
```

\pagebreak

## Relatives

<br>

```{r}
w1_rel_vars <- dat_w1_c2 %>% names() %>% str_subset("RELATIVES|_REL_") 
for(var in w1_rel_vars) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_rel_vars)
```

\pagebreak

## Friends

<br>

```{r}
w1_friends_vars <- dat_w1_c2 %>% names() %>% str_subset("FRIENDS") 
for(var in w1_friends_vars) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_friends_vars)
```

\pagebreak

## Confidante

<br>

```{r}
w1_confidante_vars <- dat_w1_c2 %>% names() %>% str_subset("CONFIDANTE") 
for(var in w1_confidante_vars) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_confidante_vars)
```

\pagebreak

## Self-Administered Questionnaire (SQX) - General

<br>

```{r sqx general}
w1_c2_wave_sqx <- dat_w1_c2 %>% names() %>% 
  str_subset("_SQX_COMPLETED|_COMMENTS_SAQXR|_SQX_METHOD")
  
for(var in w1_c2_wave_sqx) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_c2_wave_sqx)
```

\pagebreak

## SQX - Stressful Life Events

<br>

```{r sqx sle}
w1_c2_wave_sqx_sle <- dat_w1_c2 %>% names() %>% 
  str_subset("_SQX_SLE_")
  
for(var in w1_c2_wave_sqx_sle) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_c2_wave_sqx_sle)
```

\pagebreak

## SQX - Traumatic Life Events

<br>

```{r sqx tle}
w1_c2_wave_sqx_tle <- dat_w1_c2 %>% names() %>% 
  str_subset("_SQX_TLE_")
  
for(var in w1_c2_wave_sqx_tle) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_c2_wave_sqx_tle)
```

\pagebreak

## SQX - Coping Strategy

<br>

```{r sqx cs}
w1_c2_wave_sqx_cc <- dat_w1_c2 %>% names() %>% 
  str_subset("_SQX_CC_|_SQX_CS_")
  
for(var in w1_c2_wave_sqx_cc) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_c2_wave_sqx_cc)
```

\pagebreak

## SQX - Adverse Childhood Events

<br>

```{r sqx aces}
w1_c2_wave_childhx_events_age <- dat_w1_c2 %>% names() %>% 
  str_subset("_CHILDHX_EVENTS_AGE_")

w1_c2_wave_childhx_events_cat <- dat_w1_c2 %>% names() %>%
  str_subset("_CHILDHX_EVENTS_DKREFUSED_|_CHILDHX_EVENTS_YN_"  )
  
for(var in w1_c2_wave_childhx_events_cat) {
  codebook(dat_w1_c2, var)
}

for(var in w1_c2_wave_childhx_events_age) {
  codebook(dat_w1_c2, var, categorical = FALSE)
}
all_vars <- c(all_vars, w1_c2_wave_childhx_events_age, w1_c2_wave_childhx_events_cat)
```

\pagebreak

## SQX - Locus of Control

<br>

```{r self-administered questionnaire}
w1_c2_wave_sqx_loc <- dat_w1_c2 %>% names() %>% 
  str_subset("_SQX_LOC")
  
for(var in w1_c2_wave_sqx_loc) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_c2_wave_sqx_loc)
```

## Health

<br>

```{r}
w1_equipment_vars <- dat_w1_c2 %>% names() %>% str_subset("EQUIPMENT")
w1_gen_health_vars <- c("W1_SEEN_DOCTOR", "W1_SEEN_DOCTOR_TEXT", 
                        "W1_CONCENTRATING", "W1_WALKING", "W1_DRESSING", 
                        "W1_ERRANDS", "W1_HEALTH")
for(var in c(w1_gen_health_vars, w1_equipment_vars)) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_gen_health_vars, w1_equipment_vars)
```

\pagebreak

## Trust in medical researchers

<br>

```{r trust in medical researchers}
w1_c2_wave_timrs <- dat_w1_c2 %>% names() %>% 
  str_subset("_TIMRS_")
  
for(var in w1_c2_wave_timrs) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_c2_wave_timrs)
```

\pagebreak

## Religiosity

<br>

```{r religiosity}
w1_c2_wave_religion <- dat_w1_c2 %>% names() %>% 
  str_subset("_RELIGION_")
  
for(var in w1_c2_wave_religion) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_c2_wave_religion)
```

\pagebreak

## COVID-Related Questions

<br>

```{r}
w1_covid_vars <- dat_w1_c2 %>% names() %>% str_subset("COVID") %>% 
  str_subset("COVID_DIAG_ADMIT_AGE", negate = TRUE)
for(var in w1_covid_vars) {
  codebook(dat_w1_c2, var)
}

all_vars <- c(all_vars, w1_covid_vars)
```

\pagebreak

## Activities of Daily Living

<br>

```{r}
w1_adl_vars <- dat_w1_c2 %>% names() %>% str_subset("DAILY_LIVING")
for(var in w1_adl_vars) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_adl_vars)
```

\pagebreak

## Physical Activity

<br>

```{r}
w1_pa_vars <- dat_w1_c2 %>% names() %>% str_subset("_PA_") %>% 
   # need to make sure these SENAS vars don't end up in this section
  str_subset("SENAS_PA_SE|SENAS_PA_SEM", negate = TRUE)
for(var in w1_pa_vars) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_pa_vars)
```

\pagebreak

## Everyday Cognition

<br>

```{r}
w1_ecog_vars <- dat_w1_c2 %>% names() %>% str_subset("_ECOG_")
for(var in w1_ecog_vars) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_ecog_vars)
```

\pagebreak

## Sleep

<br>

```{r}
w1_sleep_vars <- dat_w1_c2 %>% names() %>% str_subset("_SLEEP_|BED|UP_MORNING|_WAKETIME_")
for(var in w1_sleep_vars) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_sleep_vars)
```

\pagebreak

## Self-Assessed Sensory Impairment

<br>

```{r}
w1_sensimp_vars <- dat_w1_c2 %>% names() %>% str_subset("_SENSIMP_")
for(var in w1_sensimp_vars) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_sensimp_vars)
```

\pagebreak

## Head Injury

<br>

```{r}
w1_headinj_vars <- dat_w1_c2 %>% names() %>% str_subset("HEAD_INJURY")
w1_headtra_vars <- dat_w1_c2 %>% names() %>% str_subset("HEAD_TRAUMA")
for(var in c(str_subset(w1_headinj_vars, "HOSP\\d"), "W1_HEAD_TRAUMA")) {
  codebook(dat_w1_c2, var)
}
for (var in c(str_subset(w1_headinj_vars, "HOSP\\d", negate = TRUE), 
              w1_headtra_vars[-1])) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_headinj_vars, w1_headtra_vars)
```


\pagebreak

## Pain

<br>

```{r}
w1_pain_vars <- dat_w1_c2 %>% names() %>% str_subset("PAIN")
for(var in w1_pain_vars) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_pain_vars)
```

\pagebreak

## Smoking

<br>

```{r}
w1_smk_vars <- dat_w1_c2 %>% names() %>% str_subset("SMK")
for(var in w1_smk_vars) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_smk_vars)
```

\pagebreak

## Alcohol Consumption

<br>

```{r}
w1_alc_vars <- dat_w1_c2 %>% names() %>% str_subset("ALC")
for(var in w1_alc_vars) {
  codebook(dat_w1_c2, var)
}
all_vars <- c(all_vars, w1_alc_vars)
```

\pagebreak

## Physical Measurements

<br>

```{r}
w1_phys_vars <- dat_w1_c2 %>% names() %>% str_subset("_PHYS_") %>% 
  str_subset("_ARMS|HARMS|HEAD|LUNG|NECK|NOTCOM_W2|PHYCMT", negate = TRUE)
w1_phys_cat <- rep(TRUE, length(w1_phys_vars))
w1_phys_cat[c(2:7,15,24:26,31,32,35:38)] <- FALSE
for(i in 1:length(w1_phys_vars)) {
  codebook(dat_w1_c2, w1_phys_vars[i], w1_phys_cat[i])
}
all_vars <- c(all_vars, w1_phys_vars)
```

\pagebreak

## NIH Toolbox

<br>

```{r}
w1_NIHTLBX_vars <- dat_w1_c2 %>% names() %>% str_subset("NIHTLBX")
codebook(dat_w1_c2, "W1_NIHTLBX_NIH_TOOLBOX")
codebook(dat_w1_c2, "W1_NIHTLBX_LANGUAGE")
for(var in str_subset(w1_NIHTLBX_vars, "NIH_TOOLBOX|f|PSMT|READ_SS|FORM|DCCS|PAT_COMP", 
                      negate = TRUE)) {
  codebook(dat_w1_c2, var, categorical = FALSE)
}
for(var in str_subset(w1_NIHTLBX_vars, "dccs|pat_comp")) {
  codebook(dat_w1_c2, var, categorical = TRUE)
}
all_vars <- c(all_vars, w1_NIHTLBX_vars)
```

\pagebreak

## SENAS

<br>

```{r}
w1_SENAS_vars <- dat_w1_c2 %>% names() %>% str_subset("SENAS")
codebook(dat_w1_c2, "W1_SENAS_SENAS")
codebook(dat_w1_c2, "W1_SENAS_VMFORM")
codebook(dat_w1_c2, "W1_SENAS_LSFORM")
codebook(dat_w1_c2, "W1_SENAS_TELEPHONE")
for(var in str_subset(w1_SENAS_vars, "SENAS_SENAS|VMFORM|LSFORM|TELEPHONE|_ON|_PA", 
                      negate = TRUE)) {
  codebook(dat_w1_c2, var, categorical = FALSE)
}
all_vars <- c(all_vars, w1_SENAS_vars)
```

\pagebreak

## Cognitive Impairment Probabilities

<br>

```{r}
w1_COGIMP_PROB_vars <- dat_w1_c2 %>% names() %>% str_subset("COGIMP_PROB")
for(var in w1_COGIMP_PROB_vars) {
  codebook(dat_w1_c2, var, categorical = FALSE)
}
all_vars <- c(all_vars, w1_COGIMP_PROB_vars)
```

\pagebreak

## Interviewer Comments

<br>

The labels for these categorical comment variables are long and many share 
the same labels. These labels are detailed at the end of this section. 

```{r}
w1_INTFDBK_vars <- dat_w1_c2 %>% names() %>% str_subset("INTFDBK")
all_vars <- c(all_vars, w1_INTFDBK_vars)
var_values_list <- c()
for(var in w1_INTFDBK_vars) {
  codebook(dat_w1_c2, var, print.values = FALSE)
  var_value <- dictionary %>% 
    filter(var_name == var) %>% 
    pull(values)
  var_values_list <- c(var_values_list, var_value)
}
var_values_label <- unique(var_values_list)
var_label_index <- c()
for (i in 1:length(var_values_list)) {
  var_label_index <- c(var_label_index, 
                       match(var_values_list[i], var_values_label))
}
```

Values Label for Interviewer Comments:

```{r}
for (i in 1:length(var_values_label)) {
  print(paste0("Label ", i))
  print(var_values_label[i])
  cat("\n\n")
}
```

```{r}
tibble(
  "Variable" = w1_INTFDBK_vars,
  "Values Label" = var_label_index
) %>% print(n = Inf)
```

```{r check}
length(names(dat_w1_c2))
names(dat_w1_c2)[!names(dat_w1_c2) %in% unique(all_vars)]
# all variables should be summarized in this codebook other than SUBJID
```