---
title: "KHANDLE Codebook"
subtitle: "Cycle 1: Wave 1 Summary"
date: "01/10/2025"
output:
  pdf_document:
    toc: true
  word_document:
    toc: true
  html_document:
    toc: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r message=FALSE}
library(tidyverse)
library(haven)
library(epiDisplay)
library(readxl)
library(lubridate)
```

```{r load dataset}
path_to_box <- "C:/Users/josephfong/Box/"

# update to the most recent data release

n_transfer <- 16
folder_date <- "2025Jan10"
file_date <- str_remove_all(as_date(folder_date), "-")

path_to_folder <- paste0(
  "KHANDLE_coded_data/Raw_data_tables/All_Wave/transfer", n_transfer, 
  "_", folder_date, "/"
)

dat <- read_sas(
  paste0(path_to_box, path_to_folder, "khandle_all_waves_", file_date, ".sas7bdat"))

dat_w1_c1 <- dat %>% 
  filter(COHORT == 1) %>% 
  dplyr::select(STUDYID, starts_with("W1"), WAVE1)
```

```{r load data dictionary, message=FALSE, warning=FALSE}
# load the data dictionary for variable name and variable description
dictionary <- read_excel(
  paste0(path_to_box, path_to_folder, 
         "KHANDLE_All_Waves_", file_date, "_Data_Dictionary.xlsx"), 
  .name_repair = "universal", 
  sheet = "Data Description") %>% 
  dplyr::select(
    all_of(c("PHI", "Variable.Name", "Variable.Label", 
             "Cycle.1.Format.Values", "Cycle.2.Format.Values"))
    # Note: choose the right format values to match the cohort/cycle
  ) %>% 
  rename("var_name" = "Variable.Name", 
         "var_desc" = "Variable.Label", 
         "values"  = "Cycle.2.Format.Values")
```


\pagebreak

Note:

For each variable, the following information is pulled from the dictionary:

*	Variable name
*	Variable description
*	Possible values and coding

A frequency table is generated to accompany most of the variables, with the 
following columns:

*	Frequency
*	%(NA+) and cum.%(NA+): relative and cumulative frequencies calculated from 
  including the NA’s in the total
*	%(NA-) and cum.%(NA-): relative and cumulative frequencies calculated from 
  excluding the NA’s from the total

If a variable is continuous in nature, a histogram is used to replace the 
frequency table, accompanied by the number of NA’s. 

\pagebreak

```{r codebook function}

codebook <- function(data, var, categorical = TRUE, print.values = TRUE) {
  # pull the variable description from the dictionary
  var_description <- dictionary %>% 
    filter(var_name == var) %>% 
    pull(var_desc)
  # pull variable coding from the dictionary
  var_values <- dictionary %>% 
    filter(var_name == var) %>% 
    pull(values)

  # print out information to be included in the codebook
  print(str_c(var, ": ", var_description))
  if (!is.na(var_values) & print.values) {print(var_values)}
  
  if(categorical) {
    # print the frequency table for categorical variables
    # with absolute, relative and cumulative frequencies
    print(str_c("Frequency table of ", var))
    tab1(data[var], graph = FALSE, cum.percent = TRUE) %>% print()
  } else {
    x <- data[var] %>% as_vector()
    na_count <- sum(is.na(x))
    na_perc <- round(na_count/length(x), digits = 3)
    print(str_c("NA Frequency: ", na_count, " (", 100*na_perc, "%)"))
    try(hist(x, main = NULL, xlab = paste(var)))
  }
  
  cat("\n\n")
 } 

# following this, we just feed variables into this function in groups
```

## Wave Information

<br>

```{r wave 1 info}
w1_wave_info_vars <- c("WAVE1", "W1_ENROLLED", "W1_COMPLETED_AT", 
                       "W1_TO_W2_DAYS", "W1_TO_W3_DAYS", "W1_TO_W4_DAYS",
                       "W1_SURVEY_SUBMISSIONSTATUS", "W1_SURVEY_TYPE", "W1_LANGUAGE")
codebook(dat_w1_c1, "WAVE1")
#codebook(dat_w1_c1, "W1_ENROLLED")
codebook(dat_w1_c1, "W1_COMPLETED_AT")
codebook(dat_w1_c1, "W1_SURVEY_SUBMISSIONSTATUS")
codebook(dat_w1_c1, "W1_SURVEY_TYPE")
codebook(dat_w1_c1, "W1_LANGUAGE")
codebook(dat_w1_c1, "W1_TO_W2_DAYS", categorical = FALSE)
codebook(dat_w1_c1, "W1_TO_W3_DAYS", categorical = FALSE)
codebook(dat_w1_c1, "W1_TO_W4_DAYS", categorical = FALSE) #added w4


# I collect the variables along the way to make sure at the end that 
# all the variables are included in the codebook
all_vars <- w1_wave_info_vars
```

\pagebreak

## Age at Interview

<br>

```{r age at interview}
w1_age_at_intv <- "W1_INTERVIEW_AGE"
codebook(dat_w1_c1, w1_age_at_intv, categorical = FALSE)
all_vars <- c(all_vars, w1_age_at_intv)
```

\pagebreak

## Education

<br>

```{r w1 education}
w1_edu_vars <- dat_w1_c1 %>% names() %>% str_subset("W1_EDU|D_EDU")
for (var in w1_edu_vars) {
  codebook(dat_w1_c1, var)
}
all_vars <- c(all_vars, w1_edu_vars)
```

\pagebreak

## Occupational History

<br>

```{r w1 occupational history}
w1_jobs_vars <- dat_w1_c1 %>% names() %>% 
  str_subset("_WORK_|_JOB_|_EMP_|_MILITARY|_RETIRED_") %>% 
  str_subset("VOLUNTEER|SQX", negate = TRUE)

codebook(dat_w1_c1, "W1_FIRST_JOB_AGE")
codebook(dat_w1_c1, "W1_FIRST_JOB_AGE_YEARS", categorical = FALSE)
for(var in w1_jobs_vars[3:23]) {
  codebook(dat_w1_c1, var)
}
for(var in w1_jobs_vars[24:25]) {
  codebook(dat_w1_c1, var, categorical = FALSE)
}
for(var in w1_jobs_vars[26:27]) {
  codebook(dat_w1_c1, var, categorical = FALSE)
}
codebook(dat_w1_c1, "W1_EMP_SUMMARY")
for(var in w1_jobs_vars[29:30]) {
  codebook(dat_w1_c1, var)
}
for(var in w1_jobs_vars[31:50]) {
  codebook(dat_w1_c1, var, categorical = FALSE)
}
codebook(dat_w1_c1, "W1_EMP_NOT_ADMIN")
codebook(dat_w1_c1, "W1_REASON_NOT_WORK_NOT_ADMIN")
all_vars <- c(all_vars, w1_jobs_vars)
```

\pagebreak

## Volunteer Work

<br>

```{r}
w1_volunteer_vars <- dat_w1_c1 %>% names() %>% str_subset("VOLUNTEER")
for(var in w1_volunteer_vars[1:3]) {
  codebook(dat_w1_c1, var)
}
codebook(dat_w1_c1, "W1_TIME_VOLUNTEER_HOURS", categorical = FALSE)
all_vars <- c(all_vars, w1_volunteer_vars)
```

\pagebreak

## Other Current Activities

<br>

```{r}
w1_ca_vars <- dat_w1_c1 %>% names() %>% str_subset("_CA_")
for(var in w1_ca_vars) {
  codebook(dat_w1_c1, var)
}
all_vars <- c(all_vars, w1_ca_vars)
```

\pagebreak

## Ethnicity

<br>

```{r}
w1_ethn_vars <- dat_w1_c1 %>% names() %>% str_subset("ETHNICITY|D_RACE")
for(var in w1_ethn_vars) {
  codebook(dat_w1_c1, var)
}
all_vars <- c(all_vars, w1_ethn_vars)
```

\pagebreak

## Immigration

<br>

```{r}
w1_immigration_vars <- dat_w1_c1 %>% names() %>% 
  str_subset("COUNTRY_BORN|US_STATE|MX_STATE|AGE_MOVED_US|D_AGE_IMMIGRATION|MOTHER|FATHER")

for(var in w1_immigration_vars[1:4]) {
  codebook(dat_w1_c1, var)
}
codebook(dat_w1_c1, "W1_AGE_MOVED_US", categorical = FALSE)
for(var in w1_immigration_vars[6:14]) {
  codebook(dat_w1_c1, var)
}
codebook(dat_w1_c1, "W1_D_AGE_IMMIGRATION", categorical = FALSE)
all_vars <- c(all_vars, w1_immigration_vars)
```

\pagebreak

## Gender and Sexual Orientation

<br>

```{r}
w1_gender_vars <- dat_w1_c1 %>% names() %>% str_subset("GENDER|ORIENTATION")
for(var in w1_gender_vars) {
  codebook(dat_w1_c1, var)
}
all_vars <- c(all_vars, w1_gender_vars)
```

\pagebreak

## Marital Status

<br>

```{r}
w1_marital_vars <- dat_w1_c1 %>% names() %>% 
  str_subset("MARITAL|SPOUSE|DIVORCE|MARRIAGE")
for(var in w1_marital_vars) {
  codebook(dat_w1_c1, var)
}
all_vars <- c(all_vars, w1_marital_vars)
```

\pagebreak

## Income and Financial Insecurity

<br>

```{r}
w1_income_vars <- dat_w1_c1 %>% names() %>% str_subset("INCOME|W1_INCMRANGE_HMNZD") %>%
  str_subset("_C2", negate = T)
for(var in w1_income_vars) {
  codebook(dat_w1_c1, var)
}
all_vars <- c(all_vars, w1_income_vars)
```

\pagebreak

## Residence History and Schools Attended

<br>

Some variables (including street address, city, and state) are marked PHI in the 
dictionary, and therefore not summarized here. 

```{r}
w1_res_vars <- dat_w1_c1 %>% names() %>% str_subset("_RES_|_RESIDENCE") 
w1_school_vars <- dat_w1_c1 %>% names() %>% str_subset("_SCHOOL_|_STA_") 
for(var in c(w1_res_vars, w1_school_vars)) {
  codebook(dat_w1_c1, var)
}

all_vars <- c(all_vars, w1_res_vars, w1_school_vars)
```

\pagebreak

## Discrimination - Everyday

<br>

```{r}
w1_disc_day_vars <- dat_w1_c1 %>% names() %>% str_subset("DISC_DAY") 
for(var in c("W1_DISCRIMINATION", w1_disc_day_vars)) {
  codebook(dat_w1_c1, var)
}
all_vars <- c(all_vars, "W1_DISCRIMINATION", w1_disc_day_vars)
```

\pagebreak

## Discrimination - Lifetime

<br>

```{r}
w1_disc_life_vars <- dat_w1_c1 %>% names() %>% str_subset("DISC_LIFE") 
for(var in w1_disc_life_vars) {
  codebook(dat_w1_c1, var)
}
all_vars <- c(all_vars, w1_disc_life_vars)
```

\pagebreak

## Ladder

<br>

```{r}
codebook(dat_w1_c1, "W1_LADDER1")
all_vars <- c(all_vars, "W1_LADDER1")
```

\pagebreak

## Children

<br>

```{r}
w1_children_vars <- dat_w1_c1 %>% names() %>% 
  str_subset("CHILDREN") %>% 
  str_subset("CHILDHX", negate = TRUE)
w1_children_cat <- rep(TRUE, length(w1_children_vars))
w1_children_cat[c(2,4,6,8)] <- FALSE
for(i in 1:length(w1_children_vars)) {
  codebook(dat_w1_c1, w1_children_vars[i], w1_children_cat[i])
}
all_vars <- c(all_vars, w1_children_vars)
```

\pagebreak

## Siblings

<br>

```{r}
w1_siblings_vars <- dat_w1_c1 %>% names() %>% str_subset("SIBLINGS") 
codebook(dat_w1_c1, "W1_SIBLINGS")
codebook(dat_w1_c1, "W1_SIBLINGS_COUNT", categorical = FALSE)
all_vars <- c(all_vars, w1_siblings_vars)
```

\pagebreak

## Relatives

<br>

```{r}
w1_rel_vars <- dat_w1_c1 %>% names() %>% str_subset("RELATIVES|_REL_") 
for(var in w1_rel_vars) {
  codebook(dat_w1_c1, var)
}
all_vars <- c(all_vars, w1_rel_vars)
```

\pagebreak

## Friends

<br>

```{r}
w1_friends_vars <- dat_w1_c1 %>% names() %>% str_subset("FRIENDS") 
for(var in w1_friends_vars) {
  codebook(dat_w1_c1, var)
}
all_vars <- c(all_vars, w1_friends_vars)
```

\pagebreak

## Confidante

<br>

```{r}
w1_confidante_vars <- dat_w1_c1 %>% names() %>% str_subset("CONFIDANTE") 
for(var in w1_confidante_vars) {
  codebook(dat_w1_c1, var)
}
all_vars <- c(all_vars, w1_confidante_vars)
```

\pagebreak

## Childhood Family History

<br>

```{r}
w1_childhx_vars <- dat_w1_c1 %>% names() %>% str_subset("CHILDHX")
w1_mat_pat_vars <- dat_w1_c1 %>% names() %>% str_subset("MATERNAL|PATERNAL")
w1_gu_vars <- dat_w1_c1 %>% names() %>% str_subset("GROWINGUP")
for(var in c(w1_childhx_vars, w1_mat_pat_vars, w1_gu_vars)) {
  codebook(dat_w1_c1, var)
}
all_vars <- c(all_vars, w1_childhx_vars, w1_mat_pat_vars, w1_gu_vars)
```

\pagebreak

## Health

<br>

```{r}
w1_equipment_vars <- dat_w1_c1 %>% names() %>% str_subset("EQUIPMENT")
for(var in c("W1_HEALTH", w1_equipment_vars)) {
  codebook(dat_w1_c1, var)
}
all_vars <- c(all_vars, "W1_HEALTH", w1_equipment_vars)
```

\pagebreak

## Healthcare seeking

<br>

```{r}
w1_seen_doc <- dat_w1_c1 %>% names() %>% str_subset("_SEEN_DOCTOR")
for(var in c(w1_seen_doc)) {
  codebook(dat_w1_c1, var)
}
all_vars <- c(all_vars, w1_seen_doc)
```

\pagebreak

## Activities of Daily Living

<br>

```{r}
w1_adl_vars <- dat_w1_c1 %>% names() %>% str_subset("DAILY_LIVING")
for(var in w1_adl_vars) {
  codebook(dat_w1_c1, var)
}
all_vars <- c(all_vars, w1_adl_vars)
```

\pagebreak

## Physical Activity

<br>

```{r}
w1_pa_vars <- dat_w1_c1 %>% names() %>% str_subset("_PA_") %>% 
   # need to make sure these SENAS vars don't end up in this section
  str_subset("SENAS_PA_SE|SENAS_PA_SEM", negate = TRUE)
for(var in w1_pa_vars) {
  codebook(dat_w1_c1, var)
}
all_vars <- c(all_vars, w1_pa_vars)
```

\pagebreak

## Everyday Cognition

<br>

```{r}
w1_ecog_vars <- dat_w1_c1 %>% names() %>% str_subset("_ECOG_")
for(var in w1_ecog_vars) {
  codebook(dat_w1_c1, var)
}
all_vars <- c(all_vars, w1_ecog_vars)
```

\pagebreak

## Sleep

<br>

```{r}
w1_sleep_vars <- dat_w1_c1 %>% names() %>% str_subset("_SLEEP_|_BED_|_BEDTIME_|_WAKETIME_|_UP_MORNING_TIME")
for(var in w1_sleep_vars) {
  codebook(dat_w1_c1, var)
}
all_vars <- c(all_vars, w1_sleep_vars)
```

\pagebreak

## Self-Assessed Sensory Impairment

<br>

```{r}
w1_sensimp_vars <- dat_w1_c1 %>% names() %>% str_subset("_SENSIMP_")
for(var in w1_sensimp_vars) {
  codebook(dat_w1_c1, var)
}
all_vars <- c(all_vars, w1_sensimp_vars)
```

\pagebreak

## Head Injury

<br>

```{r}
w1_headinj_vars <- dat_w1_c1 %>% names() %>% str_subset("HEAD_INJURY")
w1_headtra_vars <- dat_w1_c1 %>% names() %>% str_subset("HEAD_TRAUMA")
for(var in c(str_subset(w1_headinj_vars, "HOSP\\d"), 
             "W1_HEAD_INJURY_EXPLOSION", "W1_HEAD_TRAUMA")) {
  codebook(dat_w1_c1, var)
}
all_vars <- c(all_vars, w1_headinj_vars, w1_headtra_vars)
```

The following block of questions, from W1_HEAD_TRAUMA_AGE_START to 
W1_HEAD_TRAUMA_DAZED are asked if HEAD_TRAUMA = 1:[Yes]. 

```{r}
for(var in str_subset(w1_headinj_vars, "HOSP\\d|EXPLOSION", negate = TRUE)) {
  codebook(dat_w1_c1, var)
}
codebook(dat_w1_c1, "W1_HEAD_TRAUMA_AGE_START")
codebook(dat_w1_c1, "W1_HEAD_TRAUMA_AGE_START_TEXT", categorical = FALSE)
codebook(dat_w1_c1, "W1_HEAD_TRAUMA_AGE_END")
codebook(dat_w1_c1, "W1_HEAD_TRAUMA_AGE_END_TEXT", categorical = FALSE)
codebook(dat_w1_c1, "W1_HEAD_TRAUMA_UNCONSCIOUS")
codebook(dat_w1_c1, "W1_HEAD_TRAUMA_DAZED")
```

\pagebreak

## Pain

<br>

```{r}
w1_pain_vars <- dat_w1_c1 %>% names() %>% str_subset("PAIN")
for(var in w1_pain_vars) {
  codebook(dat_w1_c1, var)
}
all_vars <- c(all_vars, w1_pain_vars)
```

\pagebreak

## Smoking

<br>

```{r}
w1_smk_vars <- dat_w1_c1 %>% names() %>% str_subset("SMK")
for(var in w1_smk_vars[-3]) {
  codebook(dat_w1_c1, var)
}
codebook(dat_w1_c1, w1_smk_vars[3], categorical = FALSE)
all_vars <- c(all_vars, w1_smk_vars)
```

\pagebreak

## Alcohol Consumption

<br>

```{r}
w1_alc_vars <- dat_w1_c1 %>% names() %>% str_subset("ALC")
for(var in w1_alc_vars) {
  codebook(dat_w1_c1, var)
}
all_vars <- c(all_vars, w1_alc_vars)
```

\pagebreak

## Physical Measurements

<br>

```{r}
w1_phys_vars <- dat_w1_c1 %>% names() %>% str_subset("_PHYS_")
w1_phys_cat <- rep(TRUE, length(w1_phys_vars))
w1_phys_cat[c(2,6:11,20,22:26,28,39,41,48,49)] <- FALSE
for(i in 1:length(w1_phys_vars)) {
  codebook(dat_w1_c1, w1_phys_vars[i], w1_phys_cat[i])
}
all_vars <- c(all_vars, w1_phys_vars)
```

\pagebreak

## NIH Toolbox

<br>

```{r}
w1_NIHTLBX_vars <- dat_w1_c1 %>% names() %>% str_subset("NIHTLBX")
codebook(dat_w1_c1, "W1_NIHTLBX_NIH_TOOLBOX")
codebook(dat_w1_c1, "W1_NIHTLBX_PSMT_FORM")
for(var in str_subset(w1_NIHTLBX_vars, "NIH_TOOLBOX|PSMT_FORM", negate = TRUE)) {
  codebook(dat_w1_c1, var, categorical = FALSE)
}
all_vars <- c(all_vars, w1_NIHTLBX_vars)
```

\pagebreak

## SENAS

<br>

```{r}
w1_SENAS_vars <- dat_w1_c1 %>% names() %>% str_subset("SENAS")
codebook(dat_w1_c1, "W1_SENAS_SENAS")
codebook(dat_w1_c1, "W1_SENAS_VMFORM")
codebook(dat_w1_c1, "W1_SENAS_LSFORM")
codebook(dat_w1_c1, "W1_SENAS_TELEPHONE")
for(var in str_subset(w1_SENAS_vars, "SENAS_SENAS|VMFORM|LSFORM|TELEPHONE", 
                      negate = TRUE)) {
  codebook(dat_w1_c1, var, categorical = FALSE)
}
all_vars <- c(all_vars, w1_SENAS_vars)
```

\pagebreak

## Cognitive Impairment Probabilities 

<br>

```{r}
w1_COGIMP_PROB_vars <- dat_w1_c1 %>% names() %>% str_subset("COGIMP_PROB")
for(var in w1_COGIMP_PROB_vars) {
  codebook(dat_w1_c1, var, categorical = FALSE)
}
all_vars <- c(all_vars, w1_COGIMP_PROB_vars)
```

\pagebreak

## Interviewer Comments

<br>

The labels for these categorical comment variables are long and many share 
the same labels. These labels are detailed at the end of this section. 

```{r}
w1_INTFDBK_vars <- dat_w1_c1 %>% names() %>% str_subset("INTFDBK")
all_vars <- c(all_vars, w1_INTFDBK_vars)
var_values_list <- c()
for(var in w1_INTFDBK_vars) {
  codebook(dat_w1_c1, var, print.values = FALSE)
  var_value <- dictionary %>% 
    filter(var_name == var) %>% 
    pull(values)
  var_values_list <- c(var_values_list, var_value)
}
var_values_label <- unique(var_values_list)
var_label_index <- c()
for (i in 1:length(var_values_list)) {
  var_label_index <- c(var_label_index, 
                       match(var_values_list[i], var_values_label))
}
```

Values Label for Interviewer Comments:

```{r}
for (i in 1:length(var_values_label)) {
  print(paste0("Label ", i))
  print(var_values_label[i])
  cat("\n\n")
}
```

```{r}
tibble(
  "Variable" = w1_INTFDBK_vars,
  "Values Label" = var_label_index
) %>% print(n = Inf)
```

\pagebreak

## Variables missing from this codebook

<br>

The following variables were not included in the codebook. Normally, SUBJID should be the only variable not being tracked. Other variables are included here due to them being asked in Cycle 2, Wave 4, which uses the same naming convention as Cycle 1, Wave 4. We have omitted these variables from the codebook as they were never asked in Cycle 2. 
```{r check}
length(names(dat_w1_c1))
names(dat_w1_c1)[!names(dat_w1_c1) %in% unique(all_vars)]
# all variables should be summarized in this codebook other than SUBJID
```